Constructing the transition graphs of interacting hysterons

### 2022-07-08 Paper_draft.tex
Corrected lack of superscript for U^* in several instances
Typo correction: U_j^+ to U_j^- in line 119
Reworked argument on switching field ordering; introduction and conclusion are still unfinished

We now describe how the transition graph is constructed for a given set of switching fields $U_i^{+, -}(S)$.\\
The possible transitions from a stable state $S$ of the system are found in two steps. First, we vary the external driving $U$ until it reaches a value where a hysteron flips, which we will call $U^*$. There are two possible transitions at each state, corresponding to an increase or decrease in the driving $U$. For an increase in the driving $U$, the first hysteron to flip is that with the lowest up switching field, which we denote as $U^+(S)$:

@@

For a decrease in the driving $U$, the first hysteron to flip is that with the highest down switching field, which we call $U^-(S)$:

@@

U^* = U^-(S) = \max_{s_j = 1}U_j^+(S)

@@

After a hysteron is flipped, we let the system relax by holding the driving at $U^*$ until a new stable state is reached. Stability under the field $U^*$ means that all hysterons in phase $s_i=0$ have up switching fields higher than $U^*$, while all hysterons in phase $s_i = 1$ have down switching fields lower than $U^*$. By applying the two steps of initiation and stability to all stable states, we find the entire transition graph. \\
We now consider how the values of the switching fields can influence the transition graph at each of the two steps. For the iniation, we only compare up switching fields with up switching fields, and down switching fields with down switching fields, at the same state $S$. At the second step, we compare both up switching fields and down switching fields with the current value of the driving, which is the field $U^*$ which initiates a transition. However, $U^*$ itself given by Equations \ref{eq:globalup} and \ref{eq:globaldown}, and thus equal to one of the switching fields $U_i^{+, -}(S)$. We remark that for both steps the transition graph only depends on a set of linear inequalities $U_i(S_A) > U_j(S_B)$. It follows that the transition graph is purely determined by the order of switching fields, rather than their absolute value.\\

@@

Now suppose that the state $S$ is not stable, but is instead a part of an avalanche. Let $U*$ be the field at which the avalanche is initiated. Hysteron $i$ must then have

@@

U_i^+(S) \leq U*

@@

U_j^+(S) > U*

>>>>

In this section we discuss the crucial role of the ordering of the switching fields $U_i^{+, -}(S)$ for the topology of the corresponding transition graph. (...) Moreover, we discuss how the ordering of the switching fields provides an easy way to generate and label the transition graphs for non-interacting hysterons, while for interacting hysterons this is more challenging. (...)\\
To establish the importance of the ordering of the switching fields, we consider how a transition graph is constructed for a given set of switching fields. To start with, we ask which hysterons flip first from each state $S$, disregarding for the moment any avalanches that the initial hysteron flips might trigger\cite{grr}. To find the transitions from a state $S$, we vary the external driving $U$ until it reaches a value where a hysteron flips, which we will call $U^*$. There are two possible transitions at each state, corresponding to an increase or decrease in the driving $U$. For an increase in the driving $U$, the first hysteron to flip is that with the lowest up switching field, which we denote as $U^+(S)$:

@@

while for a decrease in the driving $U$, the first hysteron to flip is that with the highest down switching field, which we call $U^-(S)$:

@@

U^* = U^-(S) = \max_{s_j = 1}U_j^-(S)

@@

We observe that the Equations \ref{eq:globalup} and \ref{eq:globaldown} give conditions on the switching field which are linear inequalities, of the form $U_i^+(S) > U_j^+(S)$ and $U_i^-(S) > U_j^-(S)$. Notably, the linear inequalities of this form only impose an ordering between the switching fields $U_i^{+, -}(S)$. The values of the switching fields, as well as their relative distances, can be changed without changing the transition graph, so long as the ordering of the switching fields remains the same. Thus, to determine which hysterons can be flipped from each state, it is sufficient to know the ordering of the switching fields $\{U_i^{+, -}(S)\}$.\\
We now show that the ordering between the switching fields is sufficient not just to determine the first hysteron flipped from each state, but to determine the entire transition graph, including any possible avalanches.  To prove our statement, we look in detail at how a single transition is constructed. After the first hysteron has flipped, the system reaches a new state $S^{(1)}$. If the state $S^{(1)}$ is stable under $U^*$, then there is no avalanche. We call such a transition an elementary transition. If, however, the state $S^{(1)}$ is unstable, then an avalanche occurs and additional steps are required.\\
We first look at the case of an elementary transition, where the state $S^{(1)}$ is stable under the current driving $U^*$. Stability of $S^{(1)}$ under $U^*$ means that all up switching fields $U_i^+(S^{(1)})$ are higher than the current driving $U^*$:
\begin{equation}\label{eq:stableup}
U_j^+(S^{(1)}) > U^* 
while all down switching fields are lower than $U^*$:
\begin{equation}\label{eq:stabledown}
U_j^+(S^{(1)}) < U^* 
Unlike Equations \ref{eq:globalup} and \ref{eq:globaldown}, the stability conditions in  Equations \ref{eq:stableup} and \ref{eq:stabledown} do not make a direct comparison between switching fields. Rather, the switching fields at state $S^{(1)}$ are compared to the current driving, which is $U^*$. However, $U^*$ itself is given by Equations \ref{eq:globalup} and \ref{eq:globaldown}, and therefore equal to one of the switching fields $U_i^{+, -}(S)$. Thus the stability of $S^{(1)}$ depends, once again, purely on the ordering of the switching fields.\\
Next we consider the additional steps that are required when $S^{(1)}$ is unstable. The system then enters into a new state $S^{(2)}$, for which we once again need to check the stability under the current driving. The current driving is still held at $U^*$, so the stability conditions are as in Equations \ref{eq:stableup} and \ref{eq:stabledown}, except that the state $S^{(1)}$ is now replaced by $S^{(2)}$. Thus, if the state $S^{(2)}$ is stable, we obtain a set of linear inequalities as in Equations \ref{eq:stableup} and \ref{eq:stabledown}. If the state $S^{(2)}$ is unstable, then the system moves to a third state $S^{(3)}$, and in this way the system can keep iterating through states until a stable state is reached. For each new state a corresponding set of inequalities is added, and each set of inequalities thus obtained only depends on the ordering of the switching fields. Hence, any transition $S \rightarrow S^{(1)} \rightarrow ... \rightarrow S^{(l)}$, of any length $l$, is fully determined from the ordering of the switching fields.\\
Finally, we state that the full transition graph is described by a set of inequalities that is simply a combination of the conditions on the individual transitions.(...)We conclude that the corresponding transition graph for a set of switching fields only depends on the ordering of the switching fields, as described by a set of linear inequalities. We refer to the set of inequalities underlying a graph as the design inequalities\cite{vhecke2021}.\\

@@

Now suppose that the state $S$ is not stable, but is instead a part of an avalanche. Let $U^*$ be the field at which the avalanche is initiated. Hysteron $i$ must then have

@@

U_i^+(S) \leq U^*

@@

U_j^+(S) > U^*
